Package Interconnection

### 2021-09-17 paper/package_interconnection.Rmd
Incorporates author with >1 packages eventho not 1st aut.

### get author and count how many packages they write as the first author
### there are many authors who wrote >1 packages but in the same packages, here, we just extract the first author

# get first author 
pkg_nodes_tmp$author <- rm_angle(pkg_nodes_tmp$author, replacement = "")
pkg_nodes_tmp$author <- rm_square(pkg_nodes_tmp$author, replacement = "")
pkg_nodes_tmp$author <- rm_white_punctuation(pkg_nodes_tmp$author, replacement = "")
pkg_nodes_tmp$author <- ifelse(str_detect(pkg_nodes_tmp$author, "based"), "Ernesto Barrios", pkg_nodes_tmp$author)

pkg_nodes_tmp <- pkg_nodes_tmp %>%
  cSplit("author", sep = " ,") %>%
  select(c(1:2)) %>%
  rename(first_aut = author_1)

aut_gr <- pkg_nodes_tmp %>%
  group_by(first_aut) %>%
  count() %>%
  ungroup() %>%
  arrange(desc(n)) %>%
  right_join(pkg_nodes_tmp, by = "first_aut")

pkg_nodes <- aut_gr %>%
  mutate(first_author = case_when(first_aut == "Ulrike Groemping" ~ "Ulrike Groemping",
                                 first_aut == "John Lawson" ~ "John Lawson",
                                 first_aut == "Robert B. Gramacy" ~ "Robert B. Gramacy",
                                 first_aut == "Ernesto Barrios" ~ "Ernesto Barrios",
                                 first_aut == "Kevin Wright" ~ "Kevin Wright",
                                 first_aut == "Shwetank Lall" ~ "Shwetank Lall",
                                 n == 1 ~ "Other")) %>%
  mutate(first_author = factor(first_author, levels = c("Ulrike Groemping",
                                                        "John Lawson",
                                                        "Robert B. Gramacy",
                                                        "Ernesto Barrios",
                                                        "Kevin Wright",
                                                        "Shwetank Lall",
                                                        "Other"))) %>%
  select(L2, first_author)

@@

# create the graph
ggraph(routes_tidy, layout = "kk") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm')) + 
  geom_node_point(aes(color = first_author), size = 4) + 
  geom_node_text(aes(label = name), repel = TRUE, size = 3.1) +
  scale_color_manual(values = c("blue", "tomato", "magenta", "grey50", "#48C9B0", "#C0392B", "#F1C40F")) +
  theme_graph() 
```

@@

pkg_nodes_facet <- pkg_nodes %>%
  filter(first_author %in% c("Ulrike Groemping", "John Lawson", "Robert B. Gramacy", 
                             "Kevin Wright", "Shwetank Lall", "Ernesto Barrios"))

@@

ggraph(routes_tidy_facet, layout = "kk") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(3, 'mm')), 
                 end_cap = circle(3, 'mm')) + 
  geom_node_point(aes(color = first_author), size = 4) +
  geom_node_text(aes(label = name), repel = TRUE, size = 3.5) +
  theme_graph() +
  facet_nodes(~first_author) +
  scale_color_manual(values = c("blue", "tomato", "magenta", "#48C9B0", "#C0392B", "#F1C40F"), 
                     guide = "none") +
  th_foreground(foreground = "grey80",  border = TRUE) 
```

@@

```{r int-plot}
visNetwork(nodes, edges, height = "500px", width = "100%") %>%
  visOptions(selectedBy = "first_author") %>%
  visLayout(randomSeed = 123) %>%
  visEdges(shadow = FALSE,
           arrows =list(to = list(enabled = TRUE, scaleFactor = 2))) %>%
  visLegend(useGroups = F, addEdges = ledges)
```

>>>>

### get author and count how many packages they write as the first author
### there are many authors who wrote >1 packages but in the same packages, here, we just extract the first author
```

```{r network-data}

## separate author 
aut_tidy <- pkg_nodes_tmp %>%
  # separate each aut/ctb/cph for each package
  separate_rows(author, sep=", (?=[A-Z])") %>%
  # filter only role aut and filter out cph
  filter(!str_detect(author, "ctb") & !str_detect(author, "National") & !str_detect(author, "Columbia"))

# replace character inside angle and square bracket
aut_tidy$author <- rm_angle(aut_tidy$author, replacement = "")
aut_tidy$author <- rm_square(aut_tidy$author, replacement = "")

# remove contributors written as sentence
aut_tidy <- aut_tidy %>%
  mutate(author = ifelse(str_detect(author, "Contributor"), "Yves Deville",
                         ifelse(str_detect(author, "based"), "Ernesto Barrios",
                                ifelse(str_detect(author, "contributions"), "John Lawson", author))))

# extract author who wrote >1 packages
aut_group <- aut_tidy %>%
  group_by(author) %>%
  count() %>%
  arrange(desc(n))

aut_num <- filter(aut_group, n > 1)

aut_tidy_join <- left_join(aut_tidy, aut_group, by = "author") %>%
  group_by(L2) %>%
  arrange(desc(n), .by_group = TRUE)

pkg_nodes <- aggregate(author ~ L2, aut_tidy_join, FUN = toString) %>%
  mutate(note = ifelse(str_detect(author, "Ulrike"), "Groemping",
                       ifelse(str_detect(L2, "Dice"), "Dupuy, Roustant, Richet, Deville",
                              ifelse(str_detect(author, "Gramacy"), "Gramacy, Taddy",
                                     ifelse(str_detect(author, "Shwetank"), "Lall, Vhargese",
                                            ifelse(str_detect(author, "Kevin Wright"), "Wright",
                                                   ifelse(str_detect(author, "Peng Liu"), "Liu",
                                                          ifelse(str_detect(author, "Ernesto"), "Barrios", "Other"))))))))

# # get first author 
# pkg_nodes_tmp$author <- rm_angle(pkg_nodes_tmp$author, replacement = "")
# pkg_nodes_tmp$author <- rm_square(pkg_nodes_tmp$author, replacement = "")
# pkg_nodes_tmp$author <- rm_white_punctuation(pkg_nodes_tmp$author, replacement = "")
# pkg_nodes_tmp$author <- ifelse(str_detect(pkg_nodes_tmp$author, "based"), "Ernesto Barrios", pkg_nodes_tmp$author)
# 
# pkg_nodes_tmp <- pkg_nodes_tmp %>%
#   cSplit("author", sep = " ,") %>%
#   select(c(1:2)) %>%
#   rename(first_aut = author_1) 
# 
# aut_gr <- pkg_nodes_tmp %>%
#   group_by(first_aut) %>%
#   count() %>%
#   ungroup() %>%
#   arrange(desc(n)) %>%
#   right_join(pkg_nodes_tmp, by = "first_aut")
# 
# 
# pkg_nodes <- aut_gr %>%
#   mutate(first_author = case_when(
#                                  n == 1 ~ "Other")) %>%
#   mutate(first_author = factor(first_author, levels = c("Ulrike Groemping",
#                                                         "John Lawson",
#                                                         "Robert B. Gramacy",
#                                                         "Ernesto Barrios",
#                                                         "Kevin Wright",
#                                                         "Shwetank Lall",
#                                                         "Other"))) %>%
#   select(L2, first_author)

@@

# create the graph
ggraph(routes_tidy, layout = "kk") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm')) + 
  geom_node_point(aes(color = note), size = 4) + 
  geom_node_text(aes(label = name), repel = TRUE, size = 3.1) +
  #scale_color_manual(values = c("blue", "tomato", "magenta", "grey50", "#48C9B0", "#C0392B", "#F1C40F")) +
  theme_graph() 
```

@@

pkg_nodes_facet <- pkg_nodes %>%
  filter(note != "Other")

@@

ggraph(routes_tidy_facet, layout = "kk") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(3, 'mm')), 
                 end_cap = circle(3, 'mm')) + 
  geom_node_point(aes(color = note), size = 4) +
  geom_node_text(aes(label = name), repel = TRUE, size = 3.5) +
  theme_graph() +
  facet_nodes(~note) +
  #scale_color_manual(values = c("blue", "tomato", "magenta", "#48C9B0", "#C0392B", "#F1C40F"), 
                    # guide = "none") +
  th_foreground(foreground = "grey80",  border = TRUE) 
```

@@

```{r int-plot}
visNetwork(nodes, edges, height = "500px", width = "100%") %>%
  visOptions(selectedBy = "note") %>%
  visLayout(randomSeed = 123) %>%
  visEdges(shadow = FALSE,
           arrows =list(to = list(enabled = TRUE, scaleFactor = 2))) %>%
  visLegend(useGroups = F, addEdges = ledges)
```
